Home

### 2025-06-16 index.qmd
Add link.
Bin sent in a link by email.

- [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html) (New)
- [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
- [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
- [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
- My co-author [Rebecca Barter](https://rebeccabarter.com/) and I are thrilled to announce the [online release](http://vdsbook.com/) of our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), an essential source for producing trustworthy data-driven results (Feb. 28, 2024).
- ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug. JSM in Toronto, 2023.
- [What is uncertainty in today's practice of data science?](https://www.sciencedirect.com/science/article/pii/S030440762300235X?dgcid=author) (Yu, 2023). Journal of Econometrics.
- [Building trust in medical AI algorithms with veridical data science](https://link.springer.com/epdf/10.1007/s13218-023-00803-y?sharing_token=ebI2N15qM6XZUegMth-Quve4RwlQNchNByi7wbcMAY7HhSJ5V2qZIFNLqxQFZ-zTvebYYHuYBEDcXzQl7eRE1JVsvjcy_eFebw0xZW9UU9CqWdFLLGd22GvHmjiyaKtyaRMQToSpZQruTneGX1KD5rV1I5kdcOMfqUq47TrVW5E%3D) (interview of Bin Yu by Dr. Merle Behr for the German scientific journal [KI - Künstliche Intelligenz](https://www.springer.com/journal/13218)), 2023
- [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
- [Breiman Lecture (video) at NeurIPS "Veridical data Science"](https://slideslive.com/38922599/veridical-data-science) ([PCS framework](https://www.pnas.org/content/117/8/3920) and iterative random forests ([iRF](https://www.pnas.org/content/115/8/1943))), 2019; [updated slides](https://www.stat.berkeley.edu/~binyu/ps/papers2020/Breiman19-NeurIPS-yu.pdf), 2020
- [Stability](https://projecteuclid.org/euclid.bj/1377612862), Bernoulli, 2013
- [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/2), Harvard Data Science Review (HDSR), 2020.
- [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA, 2020.
- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 2020.
- [Definitions, methods and applications in interpretable machine learning](https://www.pnas.org/content/116/44/22071), PNAS, 2019
- [Data wisdom for data science (blog)](http://www.odbms.org/2015/04/data-wisdom-for-data-science/), 2015
- [IMS Presidential Address "Let us own data science"](https://imstat.org/2014/10/01/ims-presidential-address-let-us-own-data-science/), IMS Bulletin, 2014
- [Embracing statistical challenges in the IT age](https://www.tandfonline.com/doi/abs/10.1198/004017007000000254), Technometrics, 2007

>>>>

- [Veridical Data Science in Biology on July 11, 2024 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
- [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html) (New)
- [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
- [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
- [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
- My co-author [Rebecca Barter](https://rebeccabarter.com/) and I are thrilled to announce the [online release](http://vdsbook.com/) of our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), an essential source for producing trustworthy data-driven results (Feb. 28, 2024).
- ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug. JSM in Toronto, 2023.
- [What is uncertainty in today's practice of data science?](https://www.sciencedirect.com/science/article/pii/S030440762300235X?dgcid=author) (Yu, 2023). Journal of Econometrics.
- [Building trust in medical AI algorithms with veridical data science](https://link.springer.com/epdf/10.1007/s13218-023-00803-y?sharing_token=ebI2N15qM6XZUegMth-Quve4RwlQNchNByi7wbcMAY7HhSJ5V2qZIFNLqxQFZ-zTvebYYHuYBEDcXzQl7eRE1JVsvjcy_eFebw0xZW9UU9CqWdFLLGd22GvHmjiyaKtyaRMQToSpZQruTneGX1KD5rV1I5kdcOMfqUq47TrVW5E%3D) (interview of Bin Yu by Dr. Merle Behr for the German scientific journal [KI - Künstliche Intelligenz](https://www.springer.com/journal/13218)), 2023
- [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
- [Breiman Lecture (video) at NeurIPS "Veridical data Science"](https://slideslive.com/38922599/veridical-data-science) ([PCS framework](https://www.pnas.org/content/117/8/3920) and iterative random forests ([iRF](https://www.pnas.org/content/115/8/1943))), 2019; [updated slides](https://www.stat.berkeley.edu/~binyu/ps/papers2020/Breiman19-NeurIPS-yu.pdf), 2020
- [Stability](https://projecteuclid.org/euclid.bj/1377612862), Bernoulli, 2013
- [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/2), Harvard Data Science Review (HDSR), 2020.
- [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA, 2020.
- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 2020.
- [Definitions, methods and applications in interpretable machine learning](https://www.pnas.org/content/116/44/22071), PNAS, 2019
- [Data wisdom for data science (blog)](http://www.odbms.org/2015/04/data-wisdom-for-data-science/), 2015
- [IMS Presidential Address "Let us own data science"](https://imstat.org/2014/10/01/ims-presidential-address-let-us-own-data-science/), IMS Bulletin, 2014
- [Embracing statistical challenges in the IT age](https://www.tandfonline.com/doi/abs/10.1198/004017007000000254), Technometrics, 2007
